---
title: "Data Cleanup"
author: "Group C"
date: "4/2/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(tidyverse)
library(countrycode)
library(naniar)
```

#### Note
data_wdi_raw.csv & data_polity_raw.csv are raw data files. data_wdi_processed.csv & data_polity_processed.csv are the processed outputs of this data cleanup project.

## Conflict Drivers & Sources
Regime type (polity scale from -10 to 10), trade dependence (Imports as a % of GDP from WDI), and economic reliance on agriculture (Agricultural production as a % of GDP from WDI).

## Polity Data
Filtered data for only post-1960 observations. Added a column with corresponding ISO3 codes for each country, removing observations where the country didn't have an ISO3 code. Renamed "iso" and "ccode_year" columns. Filtered data for only post-2000 year observations. Created two new boolean columns for anarchy and interruption, making them true when polity == -77 or -66 respectively. Changed polity2 to 0 wherever polity == -66 or -77. Exported data into data_polity_processed.csv. 

```{r}
# Polity dataset. The important driver iS polIty2 colUmn for each coUntry and year.
polity <- read.csv("raw_data/data_polity_raw.csv")

# Filtering for only post-1960 observations
polity <- polity %>% filter(year >= 1960)

# Adding iso column with iso3 codes
polity_iso <- countrycode(polity$country, origin = "country.name", destination = "iso3c") %>% cbind(polity)
names(polity_iso)[1] <- "iso"

# Removing observations which don't have an iso3 code
polity_iso <- polity_iso %>% filter(!is.na(iso))

# Renaming columns
names(polity_iso)[2] <- "ccode_year"

polity_iso <- polity_iso %>% filter(year > 1999)

# Replace polity2 column values of -66 and -77 with 0
polity_iso$interruption <- 0 # Creating new column for interruption, set all values to 0
polity_iso$anarchy <- 0 # Creating new column for interruption, set all values to 0
# Set boolean columns according to indices where polity == -66 and -77
polity_iso[(which(polity_iso$polity == -66)), "interruption"] <- 1
polity_iso[(which(polity_iso$polity == -77)), "anarchy"] <- 1
# Replace polity2 scores where polity == -66 | -77 to 0
polity_iso[(which(polity_iso$polity == -66 | polity_iso$polity == -77)), "polity2"] <- 0

# Export data into csv
write.csv(polity_iso,"data_polity_processed.csv", row.names = FALSE)
```

## WDI Data

Merged ISO3 country codes into the wdi data frame. Filtered out observations where ISO3 code was NA. Removed redundant columns and renamed the remaining columns. ".." values were replaced with NA. Data was filtered to only show years > 1999, and then exported the wdi data frame into data_wdi_processed.csv.

```{r}
# Read in data_wdi_raw.csv
wdi <- read.csv("raw_data/data_wdi_raw.csv")

# Merging ISO code column and renaming columns
names(wdi)[1] <- "country"
wdi_temp <- wdi$country %>% countrycode(origin = "country.name", dest = "iso3c") %>% cbind(wdi) 
names(wdi_temp)[1] <- "iso"

# Filtering out NA iso observations
wdi <- wdi_temp %>% filter(!is.na(iso)) 

# Removing redundant columns
wdi <- wdi[, c(-3, -5)]

# Renamed columns
names(wdi) <- c("iso", "country", "year", "agri_percent_land_area", "agri_forestry_fishing_percent_GDP", "agri_employment_percent", "imports_percent_GDP")

# Replace .. with NAs
wdi <- wdi %>% replace_with_na(replace = list(agri_percent_land_area = "..", agri_forestry_fishing_percent_GDP = "..", imports_percent_GDP = ".."))

wdi <- wdi %>% filter(year > 1999)

# Export CSV
write.csv(wdi,"data_wdi_processed.csv", row.names = FALSE)

```

